\huge A Usability Evaluation of Tor Launcher

### 2017-03-16 pets2017-paper/pets2017-paper.tex
break up long related work paragraph and wordsmith for alignment

We do not know of any published usability studies of Tor Browser
since the introduction of Tor Launcher,
which happened in the 3.5 release in December 2013~\cite{torbrowser-35}.
Lee and Fifield ran an informal ``UX sprint''
for Tor Browser in 2015~\cite{uxsprint}, bringing together developers and users
to discover common usability problems.
In what was a precursor to the present work,
they conducted detailed walkthroughs with five participants
and identified common obstacles to using Tor Browser successfully,
including hard-to-find downloads,
bad interactions with other end-user security software,
and misleading error messages.
There are some studies that evaluated earlier forms of web browsing over Tor,
without a particular focus on configuration.
Norcie et~al.~\cite{norcie2012eliminating}, in 2012,
investigated ``stop-points''
in the installation and use of Tor Browser,
places where users' uncertainty about what to do
put them at risk of not completing a task.
Of their 25 participants, 64\% encountered at least one stop-point,
such as a long startup time, misidentified icons, or confusion with other web browsers.
Fabian et~al.~\cite{fabian2010privately}, in 2010,
estimated how much Tor's added latency harms usability
(considered separately from user interface concerns).
They measured the latency of requests to common websites with and without Tor,
and mapped the latencies to compute an expected ``cancellation rate,''
the fraction of users who would have given up waiting for a request to complete.
They estimated a median cancellation rate of 88\% for Tor, compared to 14\% for direct requests.
In 2007, Clark et~al.~\cite{clark2007usability}
used cognitive walkthroughs to evaluate four
methods of web browsing over Tor
(all of which have since been superseded by Tor Browser and Tor Launcher).
Evaluating each method against a set of guidelines,
they found that none were fully satisfactory,
though the ones that used automatic configuration did better.
In 2006, Dingledine and Mathewson~\cite{dingledine2006anonymity}
emphasized that anonymizing networks, by their nature,
require lots of users, so usability is an even greater concern
than with other security systems.
They considered a case study of the ease of installing Tor,
at a time when technically inexperienced users were just beginning to use it.

>>>>

We do not know of any published usability studies of Tor Browser
since the introduction of Tor Launcher,
which happened in the 3.5 release in December 2013~\cite{torbrowser-35}.
Lee and Fifield ran an informal ``UX sprint''
for Tor Browser in 2015~\cite{uxsprint}, bringing together developers and users
to discover common usability problems.
In what was a precursor to the present work,
they conducted detailed walkthroughs with five participants
to identify common obstacles to using Tor Browser such as hard-to-find downloads,
bad interactions with other end-user security software,
and misleading error messages.

There are studies that evaluated earlier forms of web browsing over Tor,
without a particular focus on configuration.
In 2012, Norcie et~al.~\cite{norcie2012eliminating}
investigated Tor Browser's``stop-points'' during installation and use,
which they define as places where users' uncertainty about what to do
put them at risk of not completing a task.
Of their 25 participants, 64\% encountered at least one stop-point,
such as a long startup time, misidentified icons, or confusion with other web browsers.

In 2010, Fabian et~al.~\cite{fabian2010privately}
estimated how much Tor's added latency harms usability
(considered separately from user interface concerns).
They measured the latency of requests to common websites with and without Tor,
and mapped the latencies to compute an expected ``cancellation rate,''
which they define as the fraction of users who would have given up waiting for a request to complete.
They estimated a median cancellation rate of 88\% for Tor, compared to 14\% for direct requests.

In 2007, Clark et~al.~\cite{clark2007usability}
used cognitive walkthroughs to evaluate four
methods of web browsing over Tor
(all of which have since been superseded by Tor Browser and Tor Launcher).
Evaluating each method against a set of guidelines,
they found that none were fully satisfactory,
though the ones that used automatic configuration did better.
In 2006, Dingledine and Mathewson~\cite{dingledine2006anonymity}
emphasized that anonymizing networks, by their nature,
require lots of users, so usability is an even greater concern
than with other security systems.
